Avoiding tipping points in the management of ecological systems: a non-parametric Bayesian approach

### 2013-09-20 inst/doc/nonparametric-bayes.Rmd
writing

The sudden collapse of fisheries and other ecosystems is an increasingly
widespread phenomenon and a pressing concern for ecological management
and conservation.  Ecological dyanaics are frequently complex and difficult to 
measure, making uncertainty in our understanding a prediction a persistent
challenge to effective management.

Decision-theoretic approaches provide a framework to determine the best 
sequence of actions in face of uncertainty, but only when that uncertainty
can be meaningfully quantified [@Fischer2009].

@@

Often the set of feasible states is larger than the range of the observed states.  Though a system can enter a state outside previously observed values due to stochastic effects alone (such as a particularly low or high nutrient year), this concern is most keenly felt in considering the value of actions that have not yet been applied.

Of all sources of uncertainty, this has potentially recieved the least attention.  It has most often appeared in the concept of active learning or active adaptive managment, (adaptive probing, ) where it may be valauble to intentionally force a system far from the observed values even when the expected value such actions is low, as it provides much faster learning and consequent reduction of model uncertainty that can allow greater value to be derived later on.  @Ludwig1982 show that it may be advantageous to fish an unexploited population very heavily at first to obtain a better estimate of the recruitment rate.  This intuitive strategy when a population is governed by a Ricker or Beverton-Holt-like dynamic would clearly be disasterous if instead the dynamics contained an unforseen tipping point.  The best way to learn where the edge lies may be to walk up to it, but it is also the most dangerous.

@@

- Complex dynamics
- model choice and model averaging approaches

@@

- MAP

Decision making under uncertainty is a ubiquitous challenge of natural 
resource management and conservation.  [@Glaser2013](http://doi.org/10.1111/faf.12037 "Complex dynamics may limit prediction in marine fisheries")

Here we illustrate how a stochastic dynamic programming (SDP) algorithm can 
be driven by the predictions from a Gaussian Process (GP).
This provides two distinct advantages compared with contemporary approaches.
First, using a GP sidesteps the need for an accurate model-based description
of the system dynamics (or a model choice or model-averaging approach which
introduces yet more difficulty).  
Second, unlike parametric models which can only reflect 
uncertainty in the corresponding confidence intervals or posterior distributions
of their parameters, the GP approach provides a state-space dependent representation
of uncertainty.  This permits a much greater uncertainty far from the observed data than near the observed 
data.  These features allow the GP-SDP approach to find robust management solutions 
in face of both limited data and no knolwedge of correct model structure.

- Note on "not magic": honest uncertainty + SDP

The idea that any approach can perform well without either having to
know the model or have particularly good data should immediately draw
suspicion.  The reader must bear in mind that the strength of our approach
comes not from black-box predictive power from such limited information,
but rather, by providing a more honest expression of uncertainty outside
the observed data without sacrificing the predictive capacity near the
observed data. By coupling this more accurate description of what is known
and unknown to the decision-making under uncertainty framework provided
by stochastic dynamic programming, we are able to obtain more robust
management policies than with common parameteric modeling approaches.

- Note on comparing models (via value function rather than by "fit"). _Do we need this?_

@@

- Note on terminology: "Non-parametric"  _Do we need this?_

@@

We infer posterior distributions for the parameters of each model
in a Bayesian context using Gibbs sampling (implemented in R [R]()
using jags, [jags]()).  We choose uninformative uniform priors for all
parameters (See Appendix, Figures S1-S3, and Table S1, and the R code
provided). One-step-ahead predictions of these model fits are shown in
Figure 1.

@@

@@

(State-space figure??)

@@

- All models are "good fits" to the originally observed data. 
- (Simple model choice immediately leads us astray)

@@

@@

Eacho of our models $f(S_t)$ must be estimated from training data, which
we simulate from the Allen model with parameters $r = $ ` r p[1]`, 
$K =$ ` r p[2]`, $C =$ ` r p[3]`, and  $\sigma_g =$ ` r sigma_g` 
for $T=$ `r Tobs$ timesteps, starting at initial condition $X_0 = $ `r Xo`.

@@

#### Parametric uncertainty

#### Structural Uncertainty

@@

In our example, we focus on the problem in which a manager must set
the harvest level for a marine fishery each year to maximize the net
present value of the resource, given an estimated stock size from the
year before.

@@

#### Terminology: "Non-parametric"

The term non-parametric to describe modeling approaches such as Gaussian
processes is a common source of confusion, notwithstanding the fact that
the model is still specified by parameters.  Some literature has introduced
the term "semi-parametric" in tacit acknowledgment of this, which no doubt
only contributes to the confusion.  The problem is further exacerbated by
the several meanings assigned to the term in statistics: (a) that the method 
does not assume some particular probability distribution (e.g. a non-parametric bootstrap)
or (b) that the method does not assume a fixed structure to the model.  Our 
use is that of (b), in contrast to the classical approaches that do.  The 
difference is clearest by way of example.

@@

While it would be natural (and straight forward) to condition
the GP on passing through the origin (0,0) (see appendix), the estimate
shown here is based only on the observed data. The observed data from
which each model is estimated is also shown.  The observations come
from only a limited region of state space corresponding to unharvested
or weakly harvested system.  No observations occur at the theoretical
optimum or near the tipping point.

@@

@@

<!-- On mechanistic models -->

Though simple mechanistically motivated models
may be best for the latter case [@Cuddington2013; @Geritz2012], such models 
can be not only inaccurate but misleading in quantitative decision making. This 
arises for two reasons:

1. We do not know what the correct parameter values are for the models.
1. We do not know what the correct models are for ecological systems.

@@

While non-parametric Bayesian approaches will not always be preferable 
to simple mechanistic models, we highlight three aspects of the problem
consider here that make these methods particularly valuable.  These aspects
are common to many conservation decision making problems, which thus merit
greater use of non-parametric approaches that can best take advantage of them.

While expressing larger uncertainty outside the observed data, the GP
can also provide a better fit with smaller uncertainty inside the range
of the observed data. This arises from the greater flexibility of the 
Gaussian process, which describes a large family of possible curves.  
While in a parametric context this over-fitting would be more worrisome --
a high-degree polynomial could fit the data even better -- those 
concerns are driven by the resulting parametric fit outside the data,
which may involve wild oscillations unsupported by the data.  As we 
have seen in #1, the GP is less vulnerable to such unjustified predictions
outside the data, and is meanwhile free to benefit from the greater 
fit where the data is available.

This work was partially supported by the Center for Stock Assessment
Research, a partnership between the University of California Santa Cruz
and the Fisheries Ecology Division, Southwest Fisheries Science Center,
Santa Cruz, CA and by NSF grant EF-0924195 to MM.

The appendices have not yet been assembled.  Meanwhile, code to repeat the analyses, along with a complete log of all research conducted on this project, can be found at: [https://github.com/cboettig/nonparametric-bayes](https://github.com/cboettig/nonparametric-bayes/)

@@

References
==========

>>>>

<!-- FIXME -->

The sudden collapse of fisheries and other ecosystems is an increasingly
widespread phenomenon and a pressing concern for ecological management
and conservation.  Ecological dynamics are frequently complex and difficult to 
measure, making uncertainty in our understanding a prediction a persistent
challenge to effective management. 
Decision-theoretic approaches provide a framework to determine the best 
sequence of actions in face of uncertainty, but only when that uncertainty
can be meaningfully quantified [@Fischer2009].

@@

Resource management and conservation planning seek to determine the optimal set of feasible actions to maximize the value of some objectives (see [@Halpern2012])  Process error, measurement error, implementation error [@Reed1979, @Clark1986, @Roughgarden1996, @Sethi2005].  These sources of stochasticity in turn mean that model parameters can only be estimated approximately, requiring parametric uncertainty also be considered [@Ludwig1982, ].

The three sources of uncertainty: stochasticity (in process, measurement, and implementation; though we focus on process-noise only for simplicity), parametric uncertainty, and structural uncertainty, are familiar challenges.

Of all sources of uncertainty, this last has received the least attention.[^1]

Often the set of feasible states is larger than the range of the observed states.  Though most systems subject to some degree of stochasticity can enter a state outside previously observed values by chance alone (such as a particularly low or high nutrient year), this concern is most keenly felt in the decision-theoretic context. If we are observing the fluctuations of a given fish stock over many years under a fixed harvesting pressure, we might develop and test a model that could reasonably predict the frequency of a deviation of a given size, even when such a deviation has not been previously observed.

(The same analogy might be made to predicting hurricanes or other extreme weather events from historical data, which may be more accurately predicted in a constant climate than in one being perturbed).

Given adequate observations of a system

One must consider actions or policy under which the system has not yet been observed,

<!-- What do we call this?  Extrapolation uncertainty?  Pathological Uncertainty? -->

[^1]: The concept of adaptive probing is one area that has explicitly addressed this kind of uncertainty, reaching rather opposite conclusions than what we observe here. Adaptive probing strategies follow from "Dual Control" or "Active Adaptive Management" approaches (e.g. @Ludwig1982) that can trade off short term utility by choosing actions that can reduce uncertainty.  Adaptive probing strategies arise when it is valuable to intentionally force a system far from the observed values even when the expected value such actions is low, as it provides much faster learning and consequent reduction of model uncertainty that can allow greater value to be derived later on.  For instance, @Ludwig1982 show that it may be advantageous to fish an unexploited population very heavily at first to obtain a better estimate of the recruitment rate.  This intuitive strategy when a population is governed by a Ricker or Beverton-Holt-like dynamic would clearly be disastrous if instead the dynamics contained an unforeseen tipping point.  The best way to learn where the edge lies may be to walk up to it, but it is also the most dangerous.

@@

- Complex dynamics  [@Glaser2013](http://doi.org/10.1111/faf.12037 "Complex dynamics may limit prediction in marine fisheries")

- model choice and model averaging approaches

@@

- _MAP_

Decision making under uncertainty is a ubiquitous challenge of natural 
resource management and conservation. 
Here we illustrate how a stochastic dynamic programming (SDP) algorithm can 
be driven by the predictions from a Gaussian Process (GP).
This provides two distinct advantages compared with contemporary approaches.
First, using a GP sidesteps the need for an accurate model-based description
of the system dynamics (or a model choice or model-averaging approach which
introduces yet more difficulty).  
Second, unlike parametric models which can only reflect 
uncertainty in the corresponding confidence intervals or posterior distributions
of their parameters, the GP approach provides a state-space dependent representation
of uncertainty.  This permits a much greater uncertainty far from the observed data than near the observed 
data.  These features allow the GP-SDP approach to find robust management solutions 
in face of limited data and without knowledge of the correct model structure.

-  _Note on "not magic"_: honest uncertainty + SDP

The idea that any approach can perform well without either having to
know the model or have particularly good data should immediately draw
suspicion.  The reader must bear in mind that the strength of our approach
comes not from black-box predictive power from such limited information,
but rather, by providing a more honest expression of uncertainty outside
the observed data without sacrificing the predictive capacity near the
observed data. By coupling this more accurate description of what is known
and unknown to the decision-making under uncertainty framework provided
by stochastic dynamic programming, we are able to obtain more robust
management policies than with common parametric modeling approaches.

<!--move to  much later --> 
- Note on terminology: "Non-parametric"

The term non-parametric to describe Gaussian processes (GP) is unfortunate,
given that the GP models still involve the estimation of parameters. Some 
literature thus uses the term semi-parametric, which merely adds ambiguity 
to the confusion.  Statisticians give two distinct meanings to the term: (a)
referring to a method that does not assume a distribution (e.g. non-parametric bootstrap, order statistics),
and (b) one that does not assume a fixed structure but rather depends on the 
size of the data (e.g. non-parametric regression, non-parametric hierarchical models
such as the Dirichlet process).  Our use is in the latter sense.

This non-parametric property -- having a structure that is not fixed but 
rather dependent on the data is precisely the property that makes this approach
attractive in face of the limited data sampling challenges discussed above.  
Having fit a parametric model to some data, the model is completely described
by the values (or posterior distributions) of it's parameters.  The non-parametric 
model is not captured by its parameter values or distributions alone -- the 
data points become part of the model.

- _Note on comparing models_ (via value function rather than by "fit").

_Do we need this?_

@@

@@

We infer posterior distributions for the parameters of each model
in a Bayesian context using Gibbs sampling (implemented in R [@RTeam]
using jags, [@R2jags]).  We choose uninformative uniform priors for all
parameters (See Appendix, Figures S1-S3, and Table S1, and the R code
provided). One-step-ahead predictions of these model fits are shown in
Figure 1.

@@

While it would be straight forward to condition the GP on passing through the origin (0,0), the estimate
shown here is based only on the observed data. The observed data from
which each model is estimated is also shown.  The observations come
from only a limited region of state space corresponding to unharvested
or weakly harvested system.  No observations occur at the theoretical
optimum harvest rate or near the tipping point.

@@

@@

- All models are "good fits" to the originally observed data.

- (Simple model choice immediately leads us astray)

Though simple mechanistically motivated models offer the greatest potential 
to increase our basic understanding of ecological processes [@Cuddington2013; @Geritz2012], 
such models can be not only inaccurate but misleading when relied upon in a
quantitative decision making framework.

1. We do not know what the correct models are for ecological systems.
1. We have limited data from which to estimate the model -- in particular,
   such models may be misleading in predicting the probability of outcomes
   outside the training data.

These aspects are common to many conservation decision making problems, which thus merit
greater use of non-parametric approaches that can best take advantage of them.

While expressing larger uncertainty outside the observed data, the GP
can also provide a better fit with smaller uncertainty inside the range
of the observed data. This arises from the greater flexibility of the 
Gaussian process, which describes a large family of possible curves.
Despite this flexibility, the GP can be described in relatively few 
parameters and is thus far less likely to overfit.

@@

This work was partially supported by the Center for Stock Assessment
Research, a partnership between the University of California Santa Cruz
and the Fisheries Ecology Division, Southwest Fisheries Science Center,
Santa Cruz, CA and by NSF grant EF-0924195 to MM and NSF grant DBI-1306697
to CB.

@@

Eacho of our models $f(S_t)$ must be estimated from training data, which
we simulate from the Allen model with parameters $r = $ ` r p[1]`, 
$K =$ ` r p[2]`, $C =$ ` r p[3]`, and  $\sigma_g =$ ` r sigma_g` 
for $T=$ `r Tobs$ timesteps, starting at initial condition $X_0 = $ `r Xo`. 
The training data can be seen in Figure 1.

@@

@@

We focus on the problem in which a manager must set
the harvest level for a marine fishery each year to maximize the net
present value of the resource, given an estimated stock size from the
year before.

@@

@@

@@

_rambling_

@@

<!-- On mechanistic models -->
<!-- { Seems kind of irrelevant }

@@

----------------------------------------

Code to replicate the analysis, along with complete log of this research can be found at: [https://github.com/cboettig/nonparametric-bayes](https://github.com/cboettig/nonparametric-bayes/)

@@

### 2013-09-20 inst/doc/nonparametric-bayes.tex
writing

@@

Briefly set the stage: (see related papers)

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Decision-theory / optimal control framework
\item
  Fisheries context
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Dynamic uncertainty (stochasticity)
\item
  Parametric uncertainty
\item
  Structural uncertainty
\end{itemize}

@@

\begin{itemize}
\item
  Concerns of tipping points
\item
  Danger of learning
\item
  Note on ``not magic'': honest uncertainty + SDP
\item
  Note on comparing models (via value function rather than by ``fit'')
\item
  Note on terminology: ``Non-parametric''
\end{itemize}

@@

\[ \max_{h(t)} \sum_{t \in 0}^{\infty}  \Pi_t(X_t, h) \delta^t  \]

@@

Eacho of our models $f(S_t)$ must be estimated from training data, which
we simulate from the Allen model with parameters $r = 2$, $K=8$, $C=5$
and $\sigma_g = 0.1$ for $T = 40$ timesteps, starting at initial
condition $X_0 = $.

@@

@@

Decision making under uncertainty is a ubiquitous challenge of natural
resource management and conservation.\\Here we illustrate how a
stochastic dynamic programming (SDP) algorithm can be driven by the
predictions from a Gaussian Process (GP). This provides two distinct
advantages compared with contemporary approaches. First, using a GP
sidesteps the need for an accurate model-based description of the system
dynamics (or a model choice or model-averaging approach which introduces
yet more difficulty).\\Second, unlike parametric model-fitting
approaches, which can only reflect uncertainty in the corresponding
confidence intervals or posterior distributions of the parameters, the
GP approach provides a state-space dependent representation of
uncertainty. In other words, a GP estimated from a given data set
permits a much greater uncertainty far from the observed data than it
does near the observed data.

The idea that any approach can perform well without either having to
know the model or have particularly good data should immediately draw
suspicion. The reader must bear in mind that the strength of our
approach comes not from black-box predictive power from such limited
information, but rather, by providing a more honest expression of
uncertainty outside the observed data without sacrificing the predictive
capacity near the observed data.

By coupling this more accurate description of what is known and unknown
to the decision-making under uncertainty framework provided by
stochastic dynamic programming, we are able to obtain more robust
management policies than with common parameteric modeling approaches.

@@

Unfortunately, estimates of parameter uncertainty are only as good as
the parametric models themselves. Too often, we do not understand the
system dynamics well enough to know if a model provides a good
approximation over the relevant range of states and timescales (criteria
that we loosely refer to as defining the ``right'' or ``true'' model.)
So called structural or model uncertainty is a more difficult problem
than parametric uncertainty. Typical solutions involve either model
choice or model averaging. Either approach remains limited by the degree
to which any of the proposed models are sufficiently close to the right
model.

@@

\paragraph{Comparing models}

@@

\paragraph{Background on Fisheries Context}

\paragraph{Background on Tipping points}

Non-parametric models can better represent uncertainties outside of
observed data while also better capturing the dynamics in the region
observed. Advances in the theory and computational implementations of
nonparametric methods make them ripe for such applications. We use the
classic problem of optimal harvest of a marine fishery to illustrate how
the nonparametric approach of Gaussian processes can be applied. We will
compare Bayesian implementations of both nonparametric and parametric
models, which best allow us to capture the uncertainty of model
estimation in either case and permits a more natural comparison between
approaches.

@@

In our example, we focus on the problem in which a manager must set the
harvest level for a marine fishery each year to maximize the net present
value of the resource, given an estimated stock size from the year
before. The economic value and ecological concern have made marine
fisheries the crucible for much of the founding work (Gordon 1954; Reed
1979; May et al. 1979; Ludwig and Walters 1982) in managing ecosystems
under uncertainty. Global trends (Worm et al. 2006) and controversy
(Hilborn 2007; Worm et al. 2009) have made understanding these
challenges all the more pressing.

>>>>

Model uncertainty and limited data coverage are fundamental challenges
to robust ecosystem management. These challenges are acutely highlighted
by concerns that many ecological systems may contain tipping points.
Before a collapse, we do not know where the tipping points lie, if the
exist at all. Hence, we know neither a complete model of the system
dynamics nor do we have access to data in some large region of
state-space where such a tipping point might exist. These two sources of
uncertainty frustrate state-of-the-art parametric approaches to decision
theory and optimal control. I will illustrate how a non-parametric
approach using a Gaussian Process prior provides a more flexible
representation of this inherent uncertainty. Consequently, we can adapt
the Gaussian Process prior to a stochastic dynamic programming framework
in order to make robust management predictions under both model and
uncertainty and limited data.

@@

The sudden collapse of fisheries and other ecosystems is an increasingly
widespread phenomenon and a pressing concern for ecological management
and conservation. Ecological dyanaics are frequently complex and
difficult to measure, making uncertainty in our understanding a
prediction a persistent challenge to effective management.

Decision-theoretic approaches provide a framework to determine the best
sequence of actions in face of uncertainty, but only when that
uncertainty can be meaningfully quantified {[}@Fischer2009{]}.

Uncertainty enters at many levels management

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Why fisheries
\end{itemize}

The economic value and ecological concern have made marine fisheries the
crucible for much of the founding work (Gordon 1954; Reed 1979; May et
al. 1979; Ludwig and Walters 1982) in managing ecosystems under
uncertainty. Global trends (Worm et al. 2006) and controversy (Hilborn
2007; Worm et al. 2009) have made understanding these challenges all the
more pressing.

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Dynamic uncertainty (stochasticity)
\end{itemize}

From \href{}{Clark (1976)} to \href{}{Reed (1979)}

Other sources of uncertainty \href{}{Roughgarden \& Smith 1996},
\href{}{Sethi \emph{et al.} (2005)}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Parametric uncertainty 
\end{itemize}

\href{http://doi.org/10.1016/0304-38008290023-0}{Ludwig \& Walters 1982}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Structural uncertainty 
\end{itemize}

Estimates of parameter uncertainty are only as good as the parametric
models themselves. Often we do not understand the system dynamics well
enough to know if a model provides a good approximation over the
relevant range of states and timescales (criteria that we loosely refer
to as defining the ``right'' or ``true'' model.) So called structural or
model uncertainty is a more difficult problem than parametric
uncertainty. Typical solutions involve either model choice, model
averaging, or introducing yet greater model complexity of which others
may be special cases (model averaging being one such way to construct
such a model) {[}B. K. Williams (2001); Athanassoglou and Xepapadeas
(2012); @Cressie2009{]}. Even setting aside other computational and
statistical concerns (e.g. {[}@Cressie2009{]}), these approaches do not
address our second concern - representing uncertainty outside the
observed data range.

\href{http://dx.doi.org/10.1890/07-0744.1}{@Cressie2009}.

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Limits of state space
\end{itemize}

Often the set of feasible states is larger than the range of the
observed states. Though a system can enter a state outside previously
observed values due to stochastic effects alone (such as a particularly
low or high nutrient year), this concern is most keenly felt in
considering the value of actions that have not yet been applied.

Of all sources of uncertainty, this has potentially recieved the least
attention. It has most often appeared in the concept of active learning
or active adaptive managment, (adaptive probing, ) where it may be
valauble to intentionally force a system far from the observed values
even when the expected value such actions is low, as it provides much
faster learning and consequent reduction of model uncertainty that can
allow greater value to be derived later on. Ludwig and Walters (1982)
show that it may be advantageous to fish an unexploited population very
heavily at first to obtain a better estimate of the recruitment rate.
This intuitive strategy when a population is governed by a Ricker or
Beverton-Holt-like dynamic would clearly be disasterous if instead the
dynamics contained an unforseen tipping point. The best way to learn
where the edge lies may be to walk up to it, but it is also the most
dangerous.

@@

\begin{itemize}
\item
  Concerns of tipping points
\item
  Danger of learning
\item
  MAP
\end{itemize}

Decision making under uncertainty is a ubiquitous challenge of natural
resource management and conservation.
\href{http://doi.org/10.1111/faf.12037}{@Glaser2013}

Here we illustrate how a stochastic dynamic programming (SDP) algorithm
can be driven by the predictions from a Gaussian Process (GP). This
provides two distinct advantages compared with contemporary approaches.
First, using a GP sidesteps the need for an accurate model-based
description of the system dynamics (or a model choice or model-averaging
approach which introduces yet more difficulty).\\Second, unlike
parametric models which can only reflect uncertainty in the
corresponding confidence intervals or posterior distributions of their
parameters, the GP approach provides a state-space dependent
representation of uncertainty. This permits a much greater uncertainty
far from the observed data than near the observed data. These features
allow the GP-SDP approach to find robust management solutions in face of
both limited data and no knolwedge of correct model structure.

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Note on ``not magic'': honest uncertainty + SDP
\end{itemize}

The idea that any approach can perform well without either having to
know the model or have particularly good data should immediately draw
suspicion. The reader must bear in mind that the strength of our
approach comes not from black-box predictive power from such limited
information, but rather, by providing a more honest expression of
uncertainty outside the observed data without sacrificing the predictive
capacity near the observed data. By coupling this more accurate
description of what is known and unknown to the decision-making under
uncertainty framework provided by stochastic dynamic programming, we are
able to obtain more robust management policies than with common
parameteric modeling approaches.

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Note on comparing models (via value function rather than by ``fit'').
  \emph{Do we need this?}
\end{itemize}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Note on terminology: ``Non-parametric'' \emph{Do we need this?}
\end{itemize}

@@

\[ \max_{h_t} \sum_{t \in 0}^{\infty}  \Pi_t(X_t, h_t) \delta^t  \]

@@

Eacho of our models $f(S_t)$ must be estimated from training data, which
we simulate from the Allen model with parameters $r = $
\texttt{r p{[}1{]}}, $K =$ \texttt{r p{[}2{]}}, $C =$
\texttt{r p{[}3{]}}, and $\sigma_g =$ \texttt{r sigma\_g} for $T=$

Error in base::parse(text = code, srcfile = NULL) : 1:16: unexpected ','
1: Tobs$ timesteps,
                  ^
\end{verbatim}

r Xo`.

@@

While methods that account for \emph{parametric} uncertainty can be very
successful with the right model, structural uncertainty of not knowing
what model best approximates the dynamics poses considerably greater
difficulty.

@@

@@

@@

@@

@@

In our example, we focus on the problem in which a manager must set the
harvest level for a marine fishery each year to maximize the net present
value of the resource, given an estimated stock size from the year
before.
